Background Subtraction via Deep Variation Transformation

### 2018-06-20 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	new file:   build.bat 	new file:   build.sh 	new file:   config 	modified:   deep background feature transformation learning.doc 	new file:   deeplearning_bg.rar 	new file:   deeplearning_bg/deeplearning_bg/abstract.aux 	new file:   deeplearning_bg/deeplearning_bg/abstract.bbl 	new file:   deeplearning_bg/deeplearning_bg/abstract.blg 	new file:   deeplearning_bg/deeplearning_bg/abstract.log 	new file:   deeplearning_bg/

\begin{document}
\title{Background Subtraction based on Deep Feature Transformation Learning Background Subtraction}

\author{Xinyu Ren,
        Chenqiu Zhao,
		Yongxin Ge }

@@

\begin{abstract}
% 背景建模是一个复杂的问题
Background subtraction is a fundamental problem of computer vision.
% 为什么复杂
The main challenges of background subtraction comes from the diversity and the complexity of natural scenes.
% 以前的工作是怎么做的
Plenty of previous works are proposed to handle this problem by artificial model.
% 我们是怎么做的
%Previous works in this field were proposed by designing an artificial model, 
In this paper,
we propose a self-adaption solution with the utilization of convolutional neural networks, 
and a novel background subtraction model named Deep Feature Transformation Learning is proposed.
% 动机是什么
With the motivation of finding a new representation of pixels’ historical observations in a new feature space.
% 怎么做的 XXX 这两句话介绍方法，但我实在是看不懂，你再改改
The videos are divided into fixed length image blocks, which are later transformed into the pixel’s observation patches as the input of a FCN for learning the variation of pixels.
We conduct our training and prediction processes on block level.
The architecture of the FCN is devised from the semantic segmentation problem.
% 效果好
Comparisons with several state-of-the-art algorithms in well-known benchmark show the superiority of proposed approach.
\end{abstract}

@@

\section{Introduction}
% introduction 的第一段介绍这个问题为什么有做的意义
% 这个问题的意义
Background subtraction or foreground object detection is a fundamental problem of computer vision, 
which has been developed over the last few decades.
% 难点在哪
The main challenges of this problem comes from the diversely natural scenes,
such as the illumination variation \cite{2017_REVIEW_7914756}, wrapping tree \cite{2014_CVIU_SOBRAL20144} and running water \cite{Bouwmans2014}.
% 现状是什么
Previous work already achieve well performances in the scenes with low complexity.
% 现有的方法是怎么做的
In particular,
a large numbers of studies are focus designing artificial model according to the characteristic of a particular scenes.
%　效果如何
Example, the multiple background model are proposed for dynamic background,
and the texture are used to handle the shadow of objects.
%　为什么这个问题还有做下去的意义
However,
in view of
the continuous growth in videos obtained from diversely natural scenes,
more challenging scenes are proposed for background subtraction.
%　总结，这个问题很难，还能做
It remains a challenging problem to proposed a general solution for background subtraction in all exist and potential scenes.
%
% 
% 
% robust background 
% 
% via moving cameras
% in recent years, the matter of background subtraction for
% moving cameras has attracted sustained levels of interest from
% researchers
% 
% It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.
% vehicles and humans, thus saving us huge amount of computing resources.
% Typically, Background subtraction is a binary classification task that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.

% With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes.
% However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself.
% Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion.
% for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels.
% The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.
% 第二段介绍你的解决思路

% 说明问题的本质是什么

% 以这个本质为基础来评价现存方法

% 现存方法失败的原因是什么

% 我们的方法针对这个原因怎么样了

% XXX 为什么效果会好，同时也是我们方法的创新点, 最重要的还要结合图来说，

% 总结方法的思路

% 第三段介绍具体是怎么做的
% 首先一句到两句，最多３句话总结你的方法的过程

% 补充方法的细节

% 这些细节带来的好处

% 最后整个ｌｉｓｔ把方法的contribution 列出来
The contribution of proposed approach are summarized as follows:
\begin{itemize}
    \item We proposed the Deep Feature Transformation Learning model for background subtraction in complexly natural scenes.
        % 以前怎么做的
        Unlike previous XXX
        % 我们这么做有什么好处

        % 为什么要reshape 
    \item The observations in a particular pixel are reshaped into block 
        % 这么做额目的是什么，好处什么
\end{itemize}

In order to present a better and universal solution, we proposed the Deep Pixels’ Variation Learning (DPVL) model for Background Subtraction in diversely natural scenes.
In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.
%XXX introduction 里最好不要出现公式
\begin{equation}
    sq_1 = \{p_1,p_2,\cdots, p_n\} -> sq_2 = \{f_1, f_2, \cdots, f_n\}
\end{equation}
For $sq_1$, it is a sequence of pixels' intensity, which is hard to classify which entry is foreground or background.
%
But in $sq_2$, it is more easy to classified, since the output of

In this paper, pixel’s observation patches are proposed to describe the historical observation of pixels.
And a random initialized FCN network is trained to learn the historical observation of pixels and generate a new representation in a new feature space.
We take advantage of the strong learning ability of FCN to learn a new representation of the Pixel’s observation patches in a new space where the pixels can be easily classified to background and foreground.

\section{Related Work}
%  XXX 我觉的针对方法使用的特征对方法分类比较容易。例如颜色特征，纹理特征，时空间特征,最后引出你的，特征转换
Over the last few decades, Background subtraction has been well studied. Meanwhile, a huge number of methods were proposed. These methods can be broadly categorized into pixels-based, region-based, frame-based and Deep Learning.

\subsection{A. pixels-based methods}
\label{sec_spa}
% 把你想引的论文都贴上，太多了，而且你的Zhi Zeng et al. 是ｔｍ的谁啊？？
The most widely used algorithms in Background subtraction are pixels-based methods.
And one of the famous method is Gaussian Mixture Model (GMM) \cite{Zivkovic2004}, in which a GMM is used to model the history over time of pixel’s intensity values.
It is assumed that pixels are independent from their neighbors.
Incoming pixels are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound.
For learning the parameters, that maximize the likelihood, the authors proposed an online method that approximates the Expectation Maximization (EM) algorithm.

In XXX , Mingliang Chen et al.\ \cite{2017_TPAMI_GANGWANG} propose a background subtraction algorithm using hierarchical super-pixels segmentation, spanning trees and optical flow.
Their Background model combine the GMM with constrains of temporal and spatial from optical flow and super-pixels \cite{6205760_2012_TPAMI}.

Kim et al.\ \cite{Kim2004} used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model.
This allows them efficient in memory and speed compared with other background modeling techniques.
The final foreground is detected by a distance measurement in a cylindrical color model.

In XXX, Zhi Zeng et al.
proposed an equal-qualification updating strategy to replace the maximum-negative-run-length-based filtering strategy.
Their experiments show that, the proposed method outperforms well, despite using only color information.

Elgammal et al.
introduced a probabilistic non-parametric method to model the background.
It is assumed that each background pixel is drawn from a PDF.
The PDF for each pixel is estimated with Kernel Density Estimation (KDE).

\subsection{region-based approach}
\label{sec_geo}
region-based approach assumpt that the neighbouring pixels have a similar variation as the pixel itself.

In xxx, Sriram Varadarajan et al.
propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighbourhood region.

In (PCA), classification is done by comparing a block in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.

A recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.

subspace learning method in xxx, is used to compress the background into the eigenbackground.
For each video, the mean and the covariance matrix are calculated.
After a PCA of the covariance matrix, a projection matrix is set up with M eigenvectors.
Then, incoming images are compared with their projection onto the eigenvectors.
Foreground labels are assigned to pixels with large distances, after calculating the distances between the image and the projection and comparing them with the corresponding threshold value.

Marghes et al.
used a mixed method that combines a reconstructive method (PCA) with a discriminative one (LDA) to robustly model the background.

single Gaussians are employed for foreground modeling.
By computing flux tensors, which depict variations of optical flow within a local 3D spatio-temporal volume, blob motion is detected.
With the combination of the different information from blob motion, foreground models and background models, moving and static foreground objects can be spotted.
Also, by applying edge matching, static foreground objects can be classified as ghosts or intermittent motions.

Frame-based background modeling via Principal Component Analysis (PCA) and low-rank/sparse decomposition approaches is a popular alternative to pixel-level modeling xx.
These approaches are however not ideal for surveillance applications as most rely on batch or offline processing or suffer from scaling problems.

In XXX, ss et al.
addressed scaling problems by reformulating principal component analysis for 2D images.
Meanwhile their method takes much lower memory consumption and computational cost than others.
Some online approaches have also been proposed recently, but they are still very computationally expensive.

\subsection{Algorithms based on Super-pixels}
\label{sec_sup}
A novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck.
They used a fixed background model, which was generated from a temporal median operation over N video frames.

In XXX, Yi Wang et al.
tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction.
Given 200 labelled images as training set, their model performed excellently in dataset2014.

Braham et al.
present an Deep learning-based method.
with the help of CNN, they generated a fixed background model from a temporal median operation over N video frames.
Then, a scene-specific CNN is trained with corresponding image patches from the background image.

In xxx, M.
Babaee et al.
combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which can dynamically change the parameters used in the background model based on the motion changes in the video frames.
They also used spatial-median filtering as the post processing of the network outputs.

\section{The IFB Framework}
\label{sec3}
In this section, we introduce our DPVL model that consists of a pixels-based observation patches and a novel FCN networks for background subtraction.
We explain the details of the procedures of capturing the observation patches and the architecture of network in our DPVL model.
The complete system is illustrated in Figure XXX.
We use a set of input and ground true images to generalize the Pixels’ Variation Permutations, and reshape them into fixed-size image patches as and fed into a FCN.
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.

\subsection{A. Image blocks to observation  patches}
\label{sec3_fc}
The historical observations of pixels which belong to the background are usually share a common variation pattern.
In more specific terms, the variations of pixels in background are generally keeping in some pattern.
And we want to use a FCN network to learn a new representation of pixels’ observations in a new feature space.

In order to get enough pixels’ observations, we conduct our experiment on block-level.
In this paper, we divide each video into smaller image blocks, which share a common frame length of t.
For each image blocks, it contains M*N pixels’ historical observations in a temporal sequence of t frames.
We need to take them out for later transformation as our network input.

Observation patch is purposed to take advantage of the strong learning ability of the FCNs.
And what we need is an pixel-to-pixel transformation.
More precisely, Every historical pixels’ observation in these observation patches has an corresponding transformation  at the last layer of FCNs.
Here is how we get these observation patches.
First, we transform each image block into M*N pixel’s observation series which are the  single pixels’ historical observation series in a frame length of t.
Next, we reshape the observation sequence into a rectangle image which size is $\sqrt{t}\cdot \sqrt{t}$.
That rectangle image is what we called observation patch.
The observation patches are taken as network training sample set.

Another conception about observation patches is interval sampling.
For a sequence like this: 
\begin{equation}
    p_t\{p_1,o_2,\cdots,p_n\} -> \{p_1,p_{11},p_{21}, \cdots, p_n\}
\end{equation}
where $t$
denote the sequence number of frames.
By this way, we can get an new sequence contains more temporary information  than the continuous pixel sequences.
This works well when it comes to some situation where the moving objects keep stationary for a long time.

\subsection{Fully Convolutional Network}
\label{sec3_bc}
The primary task of our network is to learn an optimal feature transform of pixel’s observation series, thus we can find a new representation which is easy for classification from raw RGB data. There needs to be a consistent one-to-one match between pixels’ observation sequence and our network output on the time series. In these circumstances, traditional convolutional network cannot meet our requirements. 
Different with those traditional ones, fully convolutional networks can take input of arbitrary size and produce correspondingly-sized output with efficient inference. FCNs have already been used in many areas like sematic segmentation and so on. Researchers found FCNs has a strong learning ability which won’t lost to the traditional ones, meanwhile, it also has a high efficient computation ability.   
FCNs utilize 1*1 kernels to take the place of fully connected layers.
Therefore, we take a fixed size of pixel’s observation patches as the input of our network. For the convenience of calculations, we transform observation sequence into observation patches.

\subsection{Network Architecture}
The architectures of our proposed FCN is illustrated in Figure xx, our network contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of 1*1.
A short calculation revealed that the network output will less 10 pixels after forward calculating.
In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing zero-padding before the training.
After the forward computing, we can get the new representation of input observation values in a new feature space.
Then, after some thresholding calculations.
Our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.

\section{Experiments}
Our experiments are conducted on the computer with Nvidia tasela K20c GPU.
 And the DeepLearning tool we use is the matconvnet-23.
4 beta.

Our FCN network is random initialized, and the training epoch is set to 20.
For each video, we divide it into image blocks, which have a fixed frame length of 144.
For each image block, M*N pixel’s historical observations were taken out, where the M and N denoted the size of images.
After a simple transformation, we can get M*N pixel’s observation patches.
Each of them contains the historical observation of a pixels in a frame length of 144.

For each video, we take only one image block to generate the observation patches as our training sample set.
The other image blocks are saved for testing.

In dataset2014, most of the videos have a number of frames over 1000, thus our training data only accounts for 5% of total dataset.
But we can still get plenty of training data cause the number of the training set based on the size of images.
For example, in the video Highway of dataset2014, the image size is 320*240, so the number of observation patches for training is 76800.
In our experiment, the finally result would be better if we slightly magnify the observation patches.
We do the same to label data, but with no 0 padding.

\subsection{Evaluation Metric and Dataset}
The subjective results of background modeling approaches based on the foreground detection binary maps.
And the general international standards is F-Measure.
F-Measure is defined as:

\begin{equation}
    F=\frac{precision \dot recall}{precision - recall}
\end{equation}
\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
\includegraphics[width=.5\textwidth]{figure/fig_roc_fg}
\DeclareGraphicsExtensions.
    \caption{The example of latex figure.}
\label{fig_FBMS_nobk}
\end{figure}

\begin{table}[!t]				% TABLE
    \caption{The example of latex table}
\label{tab_FBMS_nobk}
\centering
    \begin{tabular}{|l@{  }c@{  }c@{  }cc@{  }c@{  }c@{  }c|}
\hline
     \multirow{2}{*}{Videos} & \multicolumn{3}{c}{$\text{IFB}_{nobk}$} &  & \multicolumn{3}{c|}{IFB} \\
    \cline{2-4} \cline{6-8}
       & Re &Pr & Fm &  &  Re & Pr & Fm  \\
\hline
cats03          &   (\textbf{0.9472} ,\   &  0.5428 ,\  &   0.6901 )   &  &    (0.9063 ,\	 &  \textbf{0.7955} ,\	 &  \textbf{0.8473} )   \\
bear01          &   (\textbf{0.9854} ,\   &  0.4806 ,\  &   0.6461 )   &  &    (0.8695 ,\	 &  \textbf{0.8673} ,\	 &  \textbf{0.8684} )   \\
rabbits01       &   (\textbf{0.9530} ,\   &  0.4433 ,\  &   0.6051 )   &  &    (0.9510 ,\	 &  \textbf{0.8730} ,\	 &  \textbf{0.9103} )   \\
cars5           &   (\textbf{0.9887} ,\   &  0.3693 ,\  &   0.5378 )   &  &    (0.9437 ,\	 &  \textbf{0.7108} ,\	 &  \textbf{0.8109} )   \\
tennis          &   (\textbf{0.9364} ,\   &  0.4558 ,\  &   0.6132 )   &  &    (0.8808 ,\	 &  \textbf{0.7345} ,\	 &  \textbf{0.8010} )   \\
farm01          &   (\textbf{0.9887} ,\   &  0.3897 ,\  &   0.5591 )   &  &    (0.8954 ,\	 &  \textbf{0.7462} ,\	 &  \textbf{0.8140} )   \\
\hline                                                                                                           
Average         &   (\textbf{0.9666} ,\   &  0.4469 ,\  &   0.6086 )   &  &    (0.9078 ,\    &  \textbf{0.7879} ,\   &  \textbf{0.8420} )   \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{document}
\title{Background Subtraction via Deep Variation Transformation}

\author{Yongxin Ge, 
        Xinyu Ren, 
        Chenqiu Zhao}

% XXX there is no such command of authorruning!!!!!!
% XXX 根本就没有authorruning 命令！！！
% \authorrunning{Lecture Notes in Computer Science: Chongqing University}

@@

\begin{abstract}
One of the main challenges of foreground detection comes from the diversity and complexity of real-world scenes. 
While most of previous works in this field were proposed by designing an artificial model, we tend to present a self-adaption solution, by combining the fully convolutional networks (FCNs), which is named as the Deep Pixels Variation Learning model (DPVL). 
Our main job is to find a new representation of pixels historical observations in a new feature space. 
In this paper, videos are divided into fixed length image stacks, which are later transformed into the pixel observation matrixes as the input of a FCN for learning the variation of pixels. 
We conduct our training and prediction processes on stack level. 
The architecture of the FCN is devised from the semantic segmentation problem. 
Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ variation. 
We compare our method with some state-of-the-art methods, and the results show that the proposed approach outperform its
\end{abstract}

@@

\section{Introduction}
Background subtraction or foreground object detection, as a fundamental problem in computer vision, has been much discussed with the increasing number of outdoor cameras over the last few decades. 
It is widely used as the pre-processing step of video processing, which can help us efficiently mark the region of interest, e.g. 
vehicles and humans, thus saving us huge amount of computing resources. 
Typically, Background subtraction can be viewed as a binary classification that assigns each pixel in a video sequence with a label, for either belonging to the background or foreground scene.

With a huge number of works, existed algorithms have already achieved well performances in the scenes of low diversity or complexity, such as the indoor scenes. 
However, background Subtraction is still unsolved because of the diversity in background scenes and the changes originated from the camera itself. 
Scene variations can be in many forms such as, camera jitter, dynamic background, bad weather, illumination changes, intermittent object motion. 
This is principally because the major methods, in most cases, try to find a universal solution by generating some universal background models for later linear classification; for instance, the earlier Frame Difference Methods, trying to get a fixed image as background to classify each pixels. 
The fundamental problem lies in that linear classifier might not be powerful enough for the job, due to the complexity and the diversity of natural scenes.

In order to present a better and universal solution, we proposed the Deep Variation Transformation Learning (DVTL) model for background subtraction in diversely natural scenes. 
In our method, the main job is to transform the sequence of pixels into another sequence which is easy for classification.

For \emph{Sq}, it is a sequence of pixel variation, which is hard to classify which entry is foreground or background. 
But in \emph{Sq'}, it is more easy to classified, since the output of the network is the label of each entry in sequence.

In this paper, pixel observation matrixes are proposed to describe the historical variation of pixels. 
And a random initialized FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
We take advantage of the strong learning ability of FCN to learn a new representation of the pixel observation matrixes in a new space where the pixels can be easily classified to background and foreground.

\section{Related Work}
% XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
\cite{Bouwmans2014}
Over the last few decades, Background subtraction has been well studied. 
Meanwhile, a huge number of methods were proposed. 
These methods can be broadly categorized into pixels-based, region-based, frame-based and Deep Learning.
\subsection{pixels-based methods}
The most widely used algorithms in Background subtraction are pixels-based methods. 
And one of the famous method is Gaussian Mixture Model (GMM), in which a GMM is used to model the history over time of pixel’s intensity values. 
It is assumed that pixels are independent from their neighbors. 
Incoming pixels are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
For learning the parameters, that maximize the likelihood, the authors proposed an online method that approximates the Expectation Maximization (EM) algorithm.

In XXX , Mingliang Chen et al. 
propose a background subtraction algorithm using hierarchical superpixels segmentation, spanning trees and optical flow. 
Their Background model combine the GMM with constrains of temporal and spatial from optical flow and superpixels.

Kim et al used a codebook to record the sampling background values at each pixel, which can be seemed as a compressed representation of background model. 
This allows them efficient in memory and speed compared with other background modeling techniques. 
The final foreground is detected by a distance measurement in a cylindrical color model.
In XXX, Zhi Zeng et al. 
proposed an equal-qualification updating strategy to replace the maximum-negative-run-length-based filtering strategy. 
Their experiments show that, the proposed method outperforms well, despite using only color information.
Elgammal et al. 
introduced a probabilistic non-parametric method to model the background. 
It is assumed that each background pixel is drawn from a PDF. 
The PDF for each pixel is estimated with Kernel Density Estimation (KDE).
\subsection{region-based approach}
region-based approach assumpt that the neighboring pixels have a similar variation as the pixel itself.

In xxx, Sriram Varadarajan et al. 
propose a region-based MoG to takes in which the updated mixtures represent the scene distribution in a neighborhood region.
In (PCA), classification is done by comparing a stack in current frame to its reconstruction from PCA coefficients and declaring it as background if the reconstruction is close.
recently region based method is presented in XXX which used the statistical circular shift moments (SCSM) in image regions for change detection.
subspace learning method in xxx, is used to compress the background into the eigenbackground. 
For each video, the mean and the covariance matrix are calculated. 
After a PCA of the covariance matrix, a projection matrix is set up with M eigenvectors. 
Then, incoming images are compared with their projection onto the eigenvectors. 
Foreground labels are assigned to pixels with large distances, after calculating the distances between the image and the projection and comparing them with the corresponding threshold value.

Marghes et al. 
used a mixed method that combines a reconstructive method (PCA) with a discriminative one (LDA) to robustly model the background.
single Gaussians are employed for foreground modeling. 
By computing flux tensors, which depict variations of optical flow within a local 3D spatio-temporal volume, blob motion is detected. 
With the combination of the different information from blob motion, foreground models and background models, moving and static foreground objects can be spotted. 
Also, by applying edge matching, static foreground objects can be classified as ghosts or intermittent motions.
Frame-based background modeling via Principal Component Analysis (PCA) and low-rank/sparse decomposition approaches is a popular alternative to pixel-level modeling xx. 
These approaches are however not ideal for surveillance applications as most rely on batch or offline processing or suffer from scaling problems.

In XXX, ss et al. 
addressed scaling problems by reformulating principal component analysis for 2D images. 
Meanwhile their method takes much lower memory consumption and computational cost than others. 
Some online approaches have also been proposed recently, but they are still very computationally expensive.
\subsection{Deep learning methods}
novel approach for background subtraction with the use of CNN was proposed by Braham and Droogenbroeck. 
They used a fixed background model, which was generated from a temporal median operation over N video frames.
In XXX, Yi Wang et al. 
tried a CNN architecture combined with a Cascade model for segmentation in Background subtraction. 
Given 200 labelled images as training set, their model performed excellently in dataset2014.
Braham et al. 
present an Deep learning-based method. 
with the help of CNN, they generated a fixed background model from a temporal median operation over N video frames. 
Then, a scene-specific CNN is trained with corresponding image matrixes from the background image.
In xxx, M. 
Babaee et al. 
combine the segmentation mask from SuBSENSE algorithm and the output of Flux Tensor algorithm, which can dynamically change the parameters used in the background model based on the motion changes in the video frames. 
They also used spatial-median filtering as the post processing of the network outputs.

\section{VARIATION TRANSFORMATION}
In this section, we will elaborate on the motivation of the proposed approach and how does the variation transformation works in background subtraction.

Background subtraction is essentially an binary classification in time sequence, where pixels in a video stream are separated into two categories: foreground (cars, people or animals) and background (roads, trees or other backdrops). 
In most cases, if we print out the historical observations of a single pixel, it is not hard to see that they usually keep their stability when belonging to the background. 
However, there are some exceptions: historical observations varies regularly when belonging to some dynamic background scenes(e.g. 
waves, swaying tree leaves). 
Generally, pixels from the background are sharing some common patterns of variation.

\begin{figure}[!t]	% FIGURE: figure/fig1 
\centering
    \includegraphics[width=\linewidth]{figure/fig1}
    % 图例里描述一下。
    \caption{It is hard to separate the foreground pixels from the background precisely in a time sequence.}
    \label{variation_chart}
\end{figure}

To give an intuitive understanding of the pixel variations, we plot the historical observations and corresponding groundtruth of a single pixel in Figure.1, with the X axis showing their range of variation and the Y axis representing the time. 
As we can see, there are several lines in three colors: blue, red and green. 
The blue one is called the pixel variation curve, which containing 100 original observations. 
Accordingly, the red one, the groundtruth curve is made of a piece of groundtruth data corresponding to the observations. 
The green one, which we call the transformed variation curve, is made of the outputs of the proposed approach. 
In practice, background subtraction is to produce a prediction curve, which is as near as possible to the groundtruth carve, by given the pixel variation carve.

Under ideal conditions like indoor videos, previous methods perform quite effectively, when distributions of background and foreground observations are remarkably different and the backgrounds are normally keeping static. 
While in fact, backgrounds can be rather turbulent and dynamic due to the complexity and diversity of nature scenes. 
Especially when illumination and camouflages are involved, background and foreground observations are easily confused and mixed up.

For example, in Figure.1, it is noticeable that some foreground observations in blue line share the similarly value with background ones. 
In that case, those popular solutions will inevitably yield some sticky moments when separating the pixels in the blue line. 
Statistical methods, for instance, are no longer valid, because they only focus on establishing a statistical model for the background, while having little or no concern for the temporal coherence of these observations. 
Unfortunately, most previous methods, as far as we know, are not capable to take advantage of the temporal coherence of pixel variation. 
In other words, despite knowing that pixels from the background share some common patterns of variation in a temporal sequence, we still let the order information of sequential images all go to waste. 
To alleviate this, order information of pixels must be taken in consideration. 
More concretely, we must find an efficient method to model the patterns of background pixels variations.

In this paper, a method of background subtraction based on variation transformation are proposed. 
Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. 
Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in Figure.1. 
After thresholding, we can easily get the labels of each observation. 
The benefits from variation transformation are evident and clearly seen. 
It is hard to distinguish a foreground observation when its value are similar to the background ones. 
However, classification on the transformed variation is much convenient and intuitive, due to the advantage of temporal information. 
With the aid of deep learning method, the proposed approach can be effectively implemented.

% 公式表达
And the definition of region searching method $G(x,y)$ is shown as follows:
\begin{equation}
    G(x,y) =  \mathop{\argmin}_{}{ \lVert I_t(m,n) - I_b(x,y) \rVert_{1}  } \quad  m,n \in x,y \pm R,
\end{equation}
where $x$ and $y$ is the location of pixels. And $I_t$ is the current frame, where $t$ is the
time index.

%me
\section{BACKGROUND SUBTRACTION VIA DEEP VARIATION TRANSFORMATION}
In this section, we introduce the proposed approach that consists of a novel FCN network for background subtraction. 
We explain the details of the procedures of pixel matrixes, which is a specific form of pixel variation, and the architecture of our network.

The complete system is illustrated in Figure 1. 
Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and fed them into the network. 
After reassembling the matrixes into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure*}[!t]	% FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{Fully convolutional networks can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
    \label{flow_chart}
\end{figure*}

Given different videos, the number of frames are generally different. 
However, the size of our input is fixed, which means a sampling processing is required to keep the length of pixel variations invariant. 
Therefore, image stacks are sampled form the given videos before the pixel variations are extracted. 
The given video and image stacks can be defined as follows: 
\begin{equation}
	Given \  Video=\{ I_1,I_2,I_3,\dots,I_L\} ,
\end{equation}
\begin{equation}
Stack_{(x)}=\{I_x,I_{(x+p)},I_{(x+2p)},\dots,I_L \},\quad p*l=L,\quad 1\leq   x\leq p , 
\end{equation}
Where $I_t$ represent the frame $t$ of the given video. 
And $p$ is an integer number depended on the video frames length. 
For each video, we can produce multiple image stacks and choose one of them for the training. 
In addition, thanks to the temporal sampling, we can get compact pixel historical observations containing more temporal information than the continuous pixel sequences. 
This works well when it comes to some situation where the moving objects keep stationary for a long time.

In order to make use of the temporal information of pixel historical observations, we regard the sampled observations from a single pixel as a whole, namely the pixel variation. 
After the temporal sampling, a large number of observation sequences, or pixel variations, are extracted from the chosen stack, which is shown as follows:
\begin{equation}
Sq_{(m)}=\{P_1^m,P_2^m,P_3^m,\dots,P_n^m\},
\end{equation}
Where $P_t^m$ denotes the numerical value of pixel $m$ at frame $t$ in the chosen stack. 
Each of the pixel variation is a piece of temporal information which containing the changing patterns of background pixels. 
And each of them is of fixed length $n$. 
It is notable that the quantity of observation sequences is exactly the resolution of the given video, which means an abundance of training data can be obtained with just one image stack.

Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
However, vectors are not appropriate for the network training and learning. 
Besides, we hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
Thus we reshape the variations into pixel matrixes as the input of our network. 
A sample of pixel matrix $H$ is like this:
\begin{equation}
H=P_{i+j*d}=\begin{bmatrix}
 P_1& P_2  &\dots  &P_d \\ 
\vdots &  &  &\vdots \\ 
 P_{1+(d-1)d}& \dots & \dots & P_D
\end{bmatrix},\quad d^2=D,
\end{equation}
Pixel observations are put into the $d*d$ matrix according to the order of top to bottom and left to right. 
The parameter $i$ and $j$ represent the column and row respectively. 
And the parameter $D$ is the total frame length of a variation. 
To put it from another way, pixel matrix is just a specific form of the pixel variation. 
Although the pixel matrix and the observation sequence belong to different forms of the pixel variation, they are formed of the same components, and share the common temporal information from the pixel variation. 
Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack.

In the previous steps, videos are broken down into pixel matrixes which containing abundant background information. 
Next, the groundtruth matrixes are obtained in the same way. 
Both of them are put into the network for the training. 
However, the size of the input will decreased after the network computing. 
In order to make output the same size as input, we borrowed ideas from Image semantic segmentation, which is doing padding to the input before the training. 
After the forward computing, variations are transformed in a new space where they can be easily classified by thresholding. 
The new representation of input pixel variation is defined as:
\begin{equation}
H_p= \mathcal L (E_x (H)),
\end{equation}
Where, $H_p$ denotes the output of network, which we call the prediction matrix, the forward computation of network is represented by $L$, and $E_x$ denotes the symmetric padding of pixel matrix where we have lost none of the pixel information to make the output $H_p$ the same size as the pixel matrix $H$. 
Another advantage of symmetric padding is that the order information still remains.

For the loss function, we choose the Sigmoid Cross Entropy (SCE), which are helpful to address the learning slowdown. 
The formulation is as follows:
\begin{equation}
    \begin{aligned}
        & \ell_{H_p, H_{gt}} =  \sum\limits_{x \in X, y \in Y}^{} H_{gt}(x,y) log(Sigmoid(H_p(x,y)))  \\
        & + (1 - H_{gt}(x,y)) log(1 - Sigmoid(H_p(x,y))) \\
        & Sigmoid(x) =\frac{1}{1+e^{-x}}\  ,
    \end{aligned}
\end{equation}

Where $H_{gt}$ denotes the groundtruth matrix which is given by the corresponding GT stack. 
The SCE is calculated between the transformed matrixes and the corresponding groundtruth matrixes. 
Boundaries of moving objects and pixels that out of the region of interest are ignored in the cost function.
Finally, we get the transformed variation through the FCN, which are easier for classification. 
We globally threshold the values for each observation in order to map them to $\{0,1\}$ . 
The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases}.
\end{equation}
\begin{equation}
M(x,y)=g(H_p,r) ,
\end{equation}
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
And the major contribution is that we demonstrate the effectiveness of temporal information in background 
subtraction.

Here we make a detailed introduction to the deep learning model we used and explain why we choose it.

Different with CNNs, fully convolution neural networks (FCNs) utilize convolutional layers with $1*1$ kernels to take the place of fully connected layers, which largely resolves these above-mentioned problems. 
First and foremost, the size of outputs are adjustable in FCNs, which allows an end-to-end mapping of pixel observation sequences and network outputs on the time sequence. 
We hope to determine the label of a pixel through the comparison of its compatriot in time sequence. 
There is one more point I ought to touch on, that since the feature maps are no longer need to be converted into vectors, spatial information can be retained . 
The last but not the least, FCNs have been used in sematic segmentation and researchers found FCNs have a strong learning ability which won’t lost to the traditional ones. 
Meanwhile, it’s also a high efficient computation model.

Based on above-mentioned factors, FCN is designed as the alternative network architecture in this paper. 
The structure of our FCN for background modeling is shown in Fig.1. 
The proposed FCN contains 5 convolutional layers, 2 pool layers and a convolutional layer which have a filter size of $1*1$. 
We use the Rectified Linear Unit (ReLU) as activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.

\section{Experiments}
